
# Title: "R project"
# Author: "Shakiba Eslamimehr"
# Date: "11/27/2018"
# Output: html_document


#Project Proposal
#Combination therapy of 2 or 3 drugs targetting TB by using smeg as a model
The goal of my study was to check the effect of more than 2 antibacterial drugs on smeg as a Microbacterium Tuberculosis model since this is the closest strain to TB and TB is not easy to grow and maintain. We wanted to check if it's possible to target drug resistancy by more than one drug. 


```{r library} 
library(readxl) #get R to read excel files
library(readr)
library(dplyr)


a<- read_excel("/Users/shakiba/Desktop/Desktop/book1.xlsx") #read MIC values of col/Dox/RIF 0.78 (3D synergy)
b<- read_excel("/Users/shakiba/Desktop/Desktop/Book2.xlsx") #read MIC values of col/Dox/RIF 1.56 (3D synergy)
c<- read_excel("/Users/shakiba/Desktop/Desktop/book3.xlsx") #read MIC values of RIF/Dox (2D synergy) 


df_a <- data.frame(a) #frame the data
df_b <- data.frame(b)
df_c <- data.frame(c)
```
#Calculate FIC values of evey rows in each plate after checking if the MIC values are smaller than 0.3
3D synergy data
```{r FIC values 3D}
f1 <- function (x) {        #using loop to take fic values
  for (i in 1:nrow(x)) {    #fic values of each row
    for (j in 1:ncol(x)) {
      if (x[i,j] < 0.3) {   #check if the MIC numbers are lower than 0.3 before going to the loop
        temp = switch (
          i,
          "1" = 0.195/3.12 + 0.015625/0.4+ 0.78/3.12,   #FIC equations
          "2" = 3.12/3.12 + 0.5/0.4+ 0.78/3.12,
          "3" = 3.12/3.12 + 0.5/0.4+ 0.78/3.12,
          "4" = 0.195/3.12 + 0.015625/0.4+ 0.78/3.12,
          "5" = 0.195/3.12 + 0.015625/0.4+ 0.78/3.12,
          "6" = 0.195/3.12 + 0.015625/0.4+ 0.78/3.12,
          "7" = 0.78125/3.12 + 0.015625/0.4+ 0.78/3.12,
          "8" = 1.5625/3.12 + 0.015625/0.4+ 0.78/3.1
        )
        x[i,j] <- temp
      }  
    }
  }
  return(x)
}

df_a <- df_a[ -c(1) ]

result_a <- f1(df_a)  #FIC values of Col/Dox/RIF 0.78
View(result_a)
```

```{r FIC value 3D-1}
  f2 <- function (x) {
    for (i in 1:nrow(x)) {
      for (j in 1:ncol(x)) {
        if (x[i,j] < 0.3) {
          temp = switch (
            i,
            "1" = 0.195/3.12 + 0.015625/0.4+ 1.56/3.12,
            "2" = 0.195/3.12 + 0.015625/0.4+ 1.56/3.12,
            "3" = 0.195/3.12 + 0.015625/0.4+ 1.56/3.12,
            "4" = 0.195/3.12 + 0.015625/0.4+ 0.78/3.12,
            "5" = 0.195/3.12 + 0.015625/0.4+ 0.78/3.12,
            "6" = 1.5625/3.12 +  0.03125/0.4+ 1.56/3.12,
            "7" = 3.125/3.12 +  0.03125/0.4+ 1.56/3.12,
            "8" = 3.125/3.12 +  0.03125/0.4+ 1.56/3.12
          )
          x[i,j] <- temp
        }  
      }
    }
    return(x)
  }

df_b <- df_b[ -c(1) ]

result_b <- f2(df_b)   #FIC values of Dox/Col/RIF 1.56
View(result_b)
```

```{r FIC values 2D}
  f3 <- function (x) {    
    for (i in 1:nrow(x)) {
      for (j in 1:ncol(x)) {
        if (x[i,j] < 0.3) {
          temp = switch (
            i,
            "1" = 0.024/3.12 +0.000244/0.4,
            "2" = 0.024/3.12 +0.000244/0.4,
            "3" = 0.024/3.12 +0.000244/0.4,
            "4" = 0.024/3.12 +0.000244/0.4,
            "5" = 0.390625/3.12 +0.0625/0.4,
            "6" = 0.390625/3.12 +0.0625/0.4,
            "7" = 0.048828125/3.12 +0.125/0.4,
            "8" = 0.048828125/3.12 +0.125/0.4
          )
          x[i,j] <- temp
        }  
      }
    }
    return(x)
  }
df_c <- df_c[ -c(1) ]

result_c <- f3(df_c) #FIC values of Dox/Col
View(result_c)
```

# stastistical analysis by taking t-test on 2D synergy
```{r T test}
t.test(x=df_c$X0.125,y=df_c$X6.255E,alt="two.sided",mu = 0, paired = FALSE, var.equal = FALSE,conf.level = 0.95)
```
#Conclusion:
FIC values lower than 0.8 accepted as showing synergy effect. The study shows that the MIC values of Doxycyclin and Colistin was lowered three times compare to the single drug MICs.

#Acknowledgement 
Thanks to Dr.Sen for making me believe I can do coding step by step. Before this class I was having difficulty working with even excel! This class and specifically the final project made me confident!
